Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-18 paper/icml_drau/icml_drau.tex
.

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Making Q-learning robust to time discretization}

@@

\twocolumn[
\icmltitle{Making Q-learning robust to time discretization}

@@

\begin{abstract}
	Despite remarkable successes, \emph{Deep Reinforcement learning} (DRL) remains not robust to
	hyperparameterization, implementation details and small environment changes~(\citealt{drl_matter}, \citealt{drl_matter_bis}). 
	Overcoming this sensitivity is key to making DRL applicable to real world problems.
	In this paper, we study the sensitivity of DRL to
	time discretization in \emph{near continuous time} environments. More precisely, we show that approaches based on estimations of the
	Q-function, e.g. \emph{Deep Q-learning}~\cite{dqn} and \emph{Deep deterministic policy gradient}~\cite{ddpg}
	are sensitive to variations of time discretization.
        We detail a principled method to obtain an off-policy RL algorithm that is more robust to changes in time discretization, and demontrate this robustness empirically. 
        % We further show that a simple reparameterization of the
	% Q-function as a sum of a state value term and a \emph{small} action dependent advantage term yields an algorithm
	% much more resilient to variations of time discretization.\LB{Change last sentence to: We introduce a more resilient algorithm to variations of time discretization [We could say more, but still less that what is already there]}
\end{abstract}

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Making Deep Q-learning methods robust to time discretization}

@@

\twocolumn[
\icmltitle{Making Deep Q-learning Methods Robust to Time Discretization}

@@

\begin{abstract}
	Despite remarkable successes, \emph{Deep Reinforcement Learning}
	(DRL) is not robust to hyperparameterization, implementation
	details, or small environment changes (\citealt{drl_matter},
	\citealt{drl_matter_bis}).  Overcoming such sensitivity is key to
	making DRL applicable to real world problems.  In this paper,
	we identify
	sensitivity to \emph{time discretization} in near
	continuous-time environments as a critical factor; this covers, e.g., changing the number of
	frames per second, or the action frequency of the controller.
	Empirically, we find that
	Q-learning-based approaches such as
	\emph{Deep Q-learning}~\cite{dqn} and \emph{Deep Deterministic
	Policy Gradient}~\cite{ddpg} %are highly sensitive to variations of time discretization and
	collapse with small time steps. Formally, we prove that
	$Q$-learning does not exist in
	continuous time.
	We detail a principled way to build an
	off-policy RL algorithm that yields similar performances over a wide range
	of time
	discretizations, and confirm this robustness empirically. 
	% We further show that a simple reparameterization of the
	% Q-function as a sum of a state value term and a \emph{small}
	% action dependent advantage term yields an algorithm much more
	% resilient to variations of time discretization.\LB{Change last
	% sentence to: We introduce a more resilient algorithm to
	% variations of time discretization [We could say more, but still
	% less that what is already there]}
\end{abstract}
